---
title: "Markdown Report Example"
author: "Andrew Peters"
date: "October 19, 2018"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---

This Markdown File will serve two purposes: as a general skeleton for creating more markdown reports, and as an example of markdown code in general.

```{r, echo=F, message=F}
library(knitr)
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set-options, echo=F}
report_render_start_time <- Sys.time()
opts_chunk$set(
  results    = 'show',
  comment    = NA,
  tidy       = FALSE,
  fig.width  = 6.5,
  fig.height = 4,
  fig.path   = 'figure-png/'
)

echo_chunks <- FALSE
options(width=100) #So the output is 25% wider than the default.


read_chunk("Markdown_Report_Skeleton.R") #This allows knitr to call chunks tagged in the underlying *.R file.
```

<!-- Load the sources.  Suppress the output when loading sources. -->
```{r load-sources, echo=echo_chunks, message=FALSE}
```

<!-- Load 'sourced' R files.  Suppress the output when loading packages. -->
```{r load-packages, echo=echo_chunks, message=FALSE}
```

<!-- Load any global functions and variables declared in the R file.  Suppress the output. -->
```{r declare-globals, echo=echo_chunks, results='show', message=FALSE}
```

<!-- Declare any global functions specific to a Rmd output.  Suppress the output. -->
```{r, echo=echo_chunks, message=FALSE}
  #Put presentation-specific code in here.  It doesn't call a chunk in the codebehind file.
```

<!-- Load the datasets.   -->
```{r load-data, echo=echo_chunks, results='show', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r tweak-data, echo=echo_chunks, results='show', message=TRUE}
```

Set Up: First set of tabs {.tabset .tabset-fade}
=============================
The above sets up a set of tabs. The below creates tabs and populates them with content.

Tab 1
-----------------------------
"Example"


Tab 2
-----------------------------
"Another example"


Text Manipulation {.tabset .tabset-fade}
=============================
The above set' up a set of tabs. The below creates tabs and populates them with content.


Style
-----------------------------
*Encase within with an asterisks to italicize*  
_Also works with a beginning/ending underscore_  

**Encase within two asterisks (two at the beginning and two at the end) to embolden**  
__Also works with a beginning/ending pair of underscores__  

~~An example of text that's been crossed out~~

Can Encase a number in carrats to superscript ^2^  
A character too? ^yup!^  

[A Hyperlink: Github](https://github.com/)


Lists
-----------------------------
* unordered list item 1 (asterisk)
* unordered list item 2 (asterisk)
    + sub-item 1
    + Must begin with '+'
    + And must be indented with four spaces (not a tab)
    
1. Ordered List item 1
2. Ordered List item 2
    + Sub-item 1

Other
-----------------------------
>This is a block quote, announcing an equation for the area of a circle:

$area=\pi*r^2$

>This is a block quote, containing an equation for the area of a circle: 
$area=\pi*r^2$

Line break...?

***

The other side of a line-break

Table Header |Second Header
-------------|---------
Cell 1       |Cell 2
Cell 3       |Cell 4

Size
-----------------------------
Size is controled by beginning a line of code with between 1 and 6 '#' symbols.
The more octothorps, the smaller the text.
It seems that I can't show an example within a tab like this, because R will try to parse the pound signs as headers, which break out of tabs.


Sources
=============================

  + [R Markdown Cheat Sheet](https://www.rstudio.com/wp-content/uploads/2015/02/rmarkdown-cheatsheet.pdf)
