---
title: "Treatment on the Treated and Longitudinal Data"
author: "Andrew Peters"
date: "October 19, 2018"
output: 
  html_document:
    toc: true
    toc_float: true
    number_sections: true
---

<!--  Set the working directory to the repository's base directory; this assumes the report is nested inside of one directory.-->
```{r, echo=F, message=F}
# cat("Working directory: ", getwd())
library(knitr)
library(flexdashboard)
opts_knit$set(root.dir='../')  #Don't combine this call with any other chunk -especially one that uses file paths.
```

<!-- Set the report-wide options, and point to the external code file. -->
```{r set-options, echo=F}
report_render_start_time <- Sys.time()
opts_chunk$set(
  results    = 'show',
  comment    = NA,
  tidy       = FALSE,
  fig.width  = 6.5,
  fig.height = 4,
  fig.path   = 'figure-png/'
)

echo_chunks <- FALSE
options(width=100) #So the output is 25% wider than the default.

#This allows knitr to call chunks tagged in the underlying *.R file.
# read_chunk("./IV-and-ATT/iv_analysis_first_blush.R")
read_chunk("./IV-and-ATT/iv_analysis_first_blush.R")


```

<!-- Load 'sourced' R files.  Suppress the output when loading sources. -->
```{r load-sources, echo=echo_chunks, message=FALSE}
```

<!-- Load R packages. Suppress the output when loading packages. -->
```{r load-packages, echo=echo_chunks, message=FALSE}
```

<!-- Load any global functions and variables declared in the R file.  Suppress the output. -->
```{r declare-globals, echo=echo_chunks, results='show', message=FALSE}
```

<!-- Tweak the datasets.   -->
```{r simulate-data, echo=echo_chunks, results='show', message=TRUE}
```

TOT and Longitudinal Data {.tabset .tabset-fade}
=============================


TOT - no mixed effects
-----------------------------
### Two-Stage Least Squares Regression (TSLS)

TOT can take multiple forms depending upon whether you have records of which specific individuals are *assigned* to a specific treatment condition AND which individuals actually *received* their respective treatments.  

In the example below, and in our OSDH Data, we do, so we favor the instrumental variable analysis. This process consists of two parts:

First, fitting a linear model regressing *Treatment Received* (M) onto *Treatment Assigned* (X). In other sources, *Received* is also referred to as the endogenous variable, and *Assigned* would be referred to as the Instrument or Instrumental variable. 

Second, regress the outcome of interest (Y) onto the predicted *Received* (M_hat) values from the first stage.

```{r TSLS, echo=TRUE, results='show', message=TRUE}
```


### ivreg()

The same process can be done in one line using the ivreg() function from the AER package.
```{r ivreg, echo=echo_chunks, results='show', message=TRUE}
```

### systemfit
The Same results from systemfit()
```{r systemfit, echo=echo_chunks, results='show', message=TRUE}
```


###  Reporting TOT
What to include in report of TOT (specifically IV) analysis, according to [This Source](https://www.hhs.gov/ash/oah/sites/default/files/estimating-program-effects-on-program-participants-brief.pdf): 

  + Proportion assigned to each treatment group, and proportion of each treatment group who received their assigned treatment.
  + Evidence that the two groups are roughly equivalent.
  + If using IV methods:
    + F-statistic showing (hopefully) that *Assigned* significantly predicts *Received*
    + Standard error of LATE estimate, and p-value of the impact estimate

TSLS with lmer?
-----------------------------
My immediate guess as to how to get a TOT estimate with longitudinal data is to peform TSLS but add a random effect of individual to both stages. This means using lmer() instead of lme(). It gets me an answer. 

```{r lmer-guess, echo=TRUE, results='show', message=TRUE}
```

But I have some troubling questions:

  + If this is the right answer, why can't I find any sources doing something similar?
  + Do I add the the random id effect to the second stage lmer model or not?
  

TSLS with wfe()
-----------------------------
I get...something of an answer using the wfe() package. 
```{r wfe, echo=TRUE, results='show', message=TRUE}
```


Sources
-----------------------------
### Sources
  
  + [Estimating Program Effects on Program Participans](https://www.hhs.gov/ash/oah/sites/default/files/estimating-program-effects-on-program-participants-brief.pdf)
  + [PLM: A package for linear models for panel data](https://cran.r-project.org/web/packages/plm/plm.pdf)
  + [Relevent Stack Exchange Question](https://stats.stackexchange.com/questions/159997/2sls-for-panel-data-in-r)
  + [Fixed Effects and Differences-in-Differences](https://static1.squarespace.com/static/59371c8ad1758ebe90723e40/t/5b085292758d46948e575dc3/1527272083029/strumpf+2017-DD+and+FE.pdf)
  + [PLM](https://cran.r-project.org/web/packages/plm/plm.pdf)
  + [PLM guide](https://cran.r-project.org/web/packages/plm/vignettes/plmPackage.html)
  + [systemfit guide - is not good enough](https://cran.r-project.org/web/packages/systemfit/vignettes/systemfit.pdf)
  + [wfe package](https://cran.r-project.org/web/packages/wfe/wfe.pdf)

<!--  + [NCSS Intro to 2SLS](https://ncss-wpengine.netdna-ssl.com/wp-content/themes/ncss/pdf/Procedures/NCSS/Two-Stage_Least_Squares.pdf) -->

